Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-11-10 fib2.tex
finish MF axioms

For our purposes a \emph{surface} will be an
oriented $2$-dimensional manifold with boundary.
Each boundary component is labelled with
an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
This is the set of ``anyon labels'', and comes
equiped with an involution $\hat{}$ such that $\hat{1}=1.$
Each boundary component is oriented (either explicitly or
otherwise by using the orientation of the manifold)
and contains a distinguished point.

We will mostly be concerned with \emph{planar} such
surfaces, ie. a disc with zero or more holes.

\newcommand{\F}{\mathscr{H}} % H or F ?

@@

{\bf Axiom I.}
The disjoint union of two surfaces $M$ and $N$ 
is assocated with
the tensor product of fusion spaces:
$$
    \F(M\amalg N) = \F(M)\otimes \F(N).
$$
This is natural from the point of view of quantum
physics, where the Hilbert space of two disjoint
systems is the tensor product of the space for
each system.

{\bf Axiom II.}
The fusion space of an empty surface is one dimensional: 
$\F(\phi) \cong \mathbb{C}.$

{\bf Axiom III.}
Gluing.

>>>>

For our purposes a \emph{surface} will be an
oriented $2$-dimensional manifold with boundary.
Each boundary component is labelled with
an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
This is the set of ``anyon labels'', and comes
equiped with an involution $\hat{}$ such that $\hat{1}=1.$
%Each boundary component is oriented (either explicitly or
%otherwise by using the orientation of the manifold)
Each boundary component inherits the manifold orientation 
and contains a distinguished point.

We will mostly be concerned with \emph{planar} such
surfaces, ie. disc(s) with zero or more holes.
Note that we will not require surfaces themselves to be connected.

\newcommand{\F}{\mathscr{H}} % H or F ?
\newcommand{\C}{\mathbb{C}}

@@

{\bf Axiom I.}
The fusion space of an empty surface is one dimensional, 
$\F(\phi) \cong \C.$
For $M_a$ a disc with boundary label $a$ we have
$\F(M_1)\cong \C$ and 
$\F(M_a)\cong 0$ for $a\ne 1.$
For annulus $M_{a,b}$ with boundary labels
$a, b$ we have
$\F(M_{a,\hat{a}})\cong \C$ and 
$\F(M_{a,b})\cong 0$ for $a\ne \hat{b}.$

{\bf Axiom II.}
The disjoint union of two surfaces $M$ and $N$ 
is assocated with
the tensor product of fusion spaces:
$$
    \F(M\amalg N) \cong \F(M)\otimes \F(N).
$$
This is natural from the point of view of quantum
physics, where the Hilbert space of two disjoint
systems is the tensor product of the space for
each system.

{\bf Axiom III.}
%Gluing.
Denote a surface $M$ with (at least) two boundary
components labelled $a, b$ as $M_{a,b}$. 
Let $N$ be the surface obtained from $M$ by gluing
these two boundary components together.
If we constrain $b=\hat{a}$ then the fusion space
of $M_{a,\hat{a}}$ embedds unitarily in the fusion
space of $N.$ Moreover, there is a unitary map
$$
    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \to \F(N).
$$
A common operation is to glue two separate surfaces.
We can do this by first taking disjoint union (tensoring
the fusion spaces)
and then gluing.
